Automated Example Oriented REST API Documentation

### 2017-11-02 cisco_study/cisco_study.tex
footnotes added + removed the dashes

\chapter{Automated Example Oriented REST API Documentation at Cisco}
\label{chapter:cisco_study}

>>>>

\chapter{\texorpdfstring{Automated Example Oriented REST API Documentation at Cisco \protect\footnote{S.Sohan, C.Anslow, and F.Maurer,``Automated example oriented REST API documentation at cisco,'' in Proc. of IEEE/ACM International Conference on Software Engineering, 2017, pp. 213-222.
}}{Automated Example Oriented REST API Documentation at Cisco}}
\label{chapter:cisco_study}

### 2017-11-02 demo_paper/demo_paper.tex
all chapters added
more spell checks
footnotes added + removed the dashes

%\documentclass[conference]{IEEEtran}

%\usepackage{cite}
%\usepackage{listings}
%\usepackage{amsmath}
%\lstset{showstringspaces=false, basicstyle=\footnotesize, numbers=left, numbersep=1pt }
%\usepackage[tableposition=top]{caption}
%\ifCLASSINFOpdf
%\usepackage[pdftex]{graphicx}
%\usepackage[pdftex]{color}
%\usepackage{subcaption}
%\else
%\fi
%\usepackage{url}
%\usepackage{upquote}
%\usepackage{mdframed}
%\usepackage{balance}
%\hyphenation{op-tical net-works semi-conduc-tor}

\chapter{SpyREST in Action: An Automated RESTful API Documentation Tool}

%\author{\IEEEauthorblockN{S M Sohan, Craig Anslow, and Frank Maurer}
%\IEEEauthorblockA{Department of Computer Science\\
%University of Calgary\\
%Calgary, Alberta T2N 1N4\\
%Email: \{smsohan, craig.anslow, frank.maurer\}@ucalgary.ca  }
%}
%\maketitle

@@

%\begin{IEEEkeywords}
%RESTful API, Web API, Documentation, Automation, Example based documentation
%\end{IEEEkeywords}

%\IEEEpeerreviewmaketitle

>>>>

\chapter{\texorpdfstring{SpyREST in Action: An Automated RESTful API Documentation Tool \protect\footnote{S. Sohan, C. Anslow, and F. Maurer, ``Spyrest in action: An automated RESTful API documentation tool,'' in Proc. of IEEE/ACM International Conference on Automated Software Engineering, 2015, pp. 813-818.}}{SpyREST in Action: An Automated RESTful API Documentation Tool}}
\label{chapter:demo_paper}

@@

### 2017-11-02 spy_rest/spy_rest.tex
all chapters added
first reasonably ok pass
more spell checks
footnotes added + removed the dashes

\chapter{SpyREST: Automated RESTful API Documentation using an HTTP Proxy Server}

%\author{\IEEEauthorblockN{S M Sohan, Craig Anslow, and Frank Maurer}
%\IEEEauthorblockA{Department of Computer Science\\
%University of Calgary\\
%Calgary, Alberta T2N 1N4\\
%Email: \{smsohan, craig.anslow, frank.maurer\}@ucalgary.ca  }
%}
%\maketitle

@@

%\IEEEpeerreviewmaketitle

%\begin{IEEEkeywords}
%RESTful API, Web API, Documentation, Automation, Example based documentation
%\end{IEEEkeywords}

@@

Several related work proposed specifications for RESTful APIs. Maleshkova et al. found that a lack of a standard format to document Web APIs and manual documentation causes confusions about how to use the APIs for different use cases \cite{Maleshkova_investigating}. Espinha et al. observed that most RESTful APIs are documented manually by API developers making the documentation a less reliable one \cite{Espinha_web}. Danielsen et al. presented a vocabulary for documenting RESTful Web APIs called Web Interface Language (WIfL) \cite{Danielsen_validation}. Verborgh et at. presented RESTdesc, a Resource oriented and Hyper-link based specification for describing RESTful APIs \cite{Verborgh_functional}. Mangler et al. presented RDDL, an XML based specification for describing RESTful APIs \cite{Mangler_rddl}. Kopecky´ et al. presented hRESTS, a machine readable micro-format to describe RESTful APIs that use an alternate representation compared to WIfL \cite{Kopecky_hrests}. Ning et al. presented OmniVoke, a RESTful API based invocation engine that provides an abstraction layer for RESTful API calls to multiple APIs that follow different conventions \cite{Ning_omnivoke}. Manual configuration is required to generate these aforementioned specifications for RESTful APIs. Myers et al. recommended providing a consistent look-and-feel with explanation for the starting points and an overall map comprising of both text and diagrams, providing a browsing experience with breadcrumb trail following a hierarchy, an effective search interface, providing example code and a way to exercise the examples online without writing code \cite{Myers_study}.

>>>>

\chapter{\texorpdfstring{SpyREST: Automated RESTful API Documentation using an HTTP Proxy Server \protect\footnote{S. Sohan, C. Anslow, and F. Maurer, Spyrest: ``Automated RESTful API documentation using an HTTP proxy server,'' in Proc. of IEEE/ACM International Conference on Automated Software Engineering, 2015, pp. 271-276.}}{SpyREST: Automated RESTful API Documentation using an HTTP Proxy Server}}
\label{chapter:spy_rest}

@@

@@

Several related work proposed specifications for RESTful APIs. Maleshkova et al. found that a lack of a standard format to document Web APIs and manual documentation causes confusions about how to use the APIs for different use cases \cite{Maleshkova_investigating}. Espinha et al. observed that most RESTful APIs are documented manually by API developers making the documentation a less reliable one \cite{Espinha_web}. Danielsen et al. presented a vocabulary for documenting RESTful Web APIs called Web Interface Language (WIfL) \cite{Danielsen_validation}. Verborgh et al. presented RESTdesc, a Resource oriented and Hyper-link based specification for describing RESTful APIs \cite{Verborgh_functional}. Mangler et al. presented RDDL, an XML based specification for describing RESTful APIs \cite{Mangler_rddl}. Kopecky et al. presented hRESTS, a machine readable micro-format to describe RESTful APIs that use an alternate representation compared to WIfL \cite{Kopecky_hrests}. Ning et al. presented OmniVoke, a RESTful API based invocation engine that provides an abstraction layer for RESTful API calls to multiple APIs that follow different conventions \cite{Ning_omnivoke}. Manual configuration is required to generate these aforementioned specifications for RESTful APIs. Myers et al. recommended providing a consistent look-and-feel with explanation for the starting points and an overall map comprising of both text and diagrams, providing a browsing experience with breadcrumb trail following a hierarchy, an effective search interface, providing example code and a way to exercise the examples online without writing code \cite{Myers_study}.
